Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex
some more cleaning

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations.
We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'')
using an H$_2$ density-based clump finder.
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs.
%
In \flower, the typical MCC mass and size are $M_{\rm gas}\simeq10^{6.5}$\,\Msun and $R\simeq45-100$\,pc,
which are comparable to those found in nearby spirals and starburst galaxies.
MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way),
similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs. We find that MCCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in
clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc
($\simeq$\,0$\farcs$01), which is
within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
%mm2 [citation or derivation needed?]   ***********
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.

@@

\begin{figure*}[hptb]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}:
    projected stellar mass distribution during {\it (a)} an early
    accreting phase;  {\it (b)} a major starburst following a merger
    event; and {\it (c)} a relatively quiescent post-starburst
    phase.
\label{fig:SFH}}
\end{figure*}

@@

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
identified as a single component at low $n_{\rm cut}$. This main disk
component
%mm2 occupy the top right   [left not right!]
          occupies the top left
corner of \Fig{stellarRatio16}, with a low gas mass fraction of
$f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is
dominated by bulk
%mm2 motions,
rotational motion,
as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the
velocity dispersions of most MCCs in the accreting phase of \flower
are dominated by turbulent motions,
%mm2 . On the other hand, [the first hand is missing]
  while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
  least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
%mm2 in the quiescent disk-like phase.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.

@@

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main
disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential
influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with
virial parameter comparable to some of the molecular structures
observed in the Milky Way,
%mm2 but the former is
     though the MCCs are
     more massive.

@@

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however,
MCCs in the starburst phase span a wider range in gas surface density
(bottom panels of \Fig{larsons_single}) and have lower virial parameters.
That is, MCCs in the starburst phase are more susceptible to collapse, as expected.
The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood
of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby
ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%

@@

We investigate possible variations in the dynamics of the molecular structures of \flower
by adopting different
%mm2 sets
    values
of $n_{\rm cut}$ % in identifying the MCCs
to test the robustness of our results against the choice of density threshold.
That is, how sensitively are the structure properties, and thus, the
results presented in \Sec{singless}, dependent on the choice of density thresholds?

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways.
As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds
corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher
$n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$
 since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$
(see top panels of \Fig{alpha16-28}).
At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
%
The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$.
This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in
nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies,
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}).
However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature
are probably limited by the spatial resolution.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%mm2
   This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to
   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
   higher velocities likely being produced by Toomre instability driven radial inflow.

@@

\subsection{Toomre Parameter and Stability of MCCs} \label{sec:Qeff}
\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0_2.0}.pdf}
\caption{
Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and
their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels).
Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols
as an illustrative example.
\label{fig:sigma}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
\caption{
Toomre $Q$ maps derived from the central $R$\eq1.2\,kpc of \flower. Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively. The effective two-component Toomre $Q_{\rm eff}$ parameter map is shown in the right panel.
%
All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
%
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols.
%A divergent colormap is used for the Toomre $Q$ maps to facilitate identification of regions above and below $\log{Q}$\eq0.
Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
%
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region}
reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations
in relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}

@@

% \AP{I think we should add a in-text comparison with the following \citet{grisdale:2017,grisdale:2018,grisdale:2019}, particularly the \citet{grisdale:2017}, similarly to what we have done for \citet{Behrendt16a}}

@@

High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their
central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that
funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand,
the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows.
The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive
MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.

The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}. This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.

% where the virial parameter is used as a surrogate for comparing the potential to kinetic energies of molecule gas structures.
We perform virial analysis, as motivated by \obs, to assess the stability of MCCs. On average, the virial parameter of MCCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF. Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower density thresholds.

% Toomre:
Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against axisymmetric perturbations, especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also non-negligible. This illustrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
%
Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates. This is consistent with the notion that collapsing structures result from gravitational instability occurring within globally stable structures, which are supported by turbulence and rotation on large scale.
This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
With the Next Generation VLA (ngVLA), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
% 0.005" highest freq
In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.

>>>>

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations. We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
%
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs. In \flower, the typical MCC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies. MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs. We find that MCCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
%
Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.

@@

\begin{figure*}[hptb]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/sfh.pdf}
\caption{
    {\it Top}: Star formation history of \flower. {\it Bottom}: projected stellar mass distribution during {\it (a)} an early accreting phase;
    %
    {\it (b)} a major starburst following a merger event; and {\it (c)} a relatively quiescent post-starburst phase.
    \label{fig:SFH}
   }
\end{figure*}

@@

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$. This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is dominated by bulk rotational motion, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions, while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.

@@

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way, though the MCCs are more massive.

@@

% Starburst
In the starburst phase, MCCs have velocity dispersion and sizes similar to those in the accreting phase; however, MCCs in the starburst phase span a wider range in gas surface density (bottom panels of \Fig{larsons_single}) and have lower virial parameters.
%
That is, MCCs in the starburst phase are more susceptible to collapse, as expected. The gas surface density of MCCs in both accreting and starburst phases is higher than that in the solar neighborhood of the Milky Way and the Large Magellanic Cloud (LMC), but comparable to those observed in starburst galaxies and the nearby ultra-luminous IR galaxies \citep[ULIRGS;][]{Boulares90a, Scoville91a, Weiss01a, Hughes10a, Leroy15a}.
% LMC: 0.01 g cm^-2
% M82: 0.1 g cm^-2
% Arp 220: 7-20 g cm^-2
%

@@

\AP{let us recall to make the not about different molecular tracers also here}
We investigate possible variations in the dynamics of the molecular structures of \flower by adopting different values of $n_{\rm cut}$ to test the robustness of our results against the choice of density threshold. That is, how sensitively are the structure properties, and thus, the results presented in \Sec{singless}, dependent on the choice of density thresholds?

The sizes of MCCs are dependent on the choice of $n_{\rm cut}$ in the following ways. As mentioned in \Sec{dist}, the most massive cloud identified at low H$_2$ gas density thresholds corresponds to the molecular disk of \flower, which is broken down into multiple smaller MCCs at higher $n_{\rm cut}$\footnote{That said, there are fewer MCCs at highest $n_{\rm cut}$ than the lowest $n_{\rm cut}$ since there are fewer cells in the simulations with correspondingly high H$_2$ gas densities.}.
%
Second, excluding such structure, some MCCs are further broken down into smaller MCCs at higher $n_{\rm cut}$ (see top panels of \Fig{alpha16-28}). At the resolution limit of our simulation, most MCCs studied in this work have $R\simeq$\,50\,pc (see also \Fig{dist}).
%
The gas velocity dispersion $\sigma_{\rm gas}$ of MCCs, on the other hand, is rather insensitive to the actual value of $n_{\rm cut}$. This lack of variation is reassuring: our inference on the velocity dispersion of \z$\sim$\,6 MCCs in relation to those observed in nearby and \z$\sim$2 galaxies is not biased by our choice of $n_{\rm cut}$ in this work.

@@

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). However, the sizes of MCCs are almost a factor of two smaller. This suggests that the sizes of \highz molecular gas structures reported in the literature are probably limited by the spatial resolution.
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%
This contrasts with \citet{Krumholz18a}, who show that numerical models and analytic arguments point to feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with higher velocities likely being produced by Toomre instability driven radial inflow.

@@

\subsection{Toomre Parameter and Stability of MCCs} \label{sec:Qeff}

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{\figpath/{ss16_toomre_combined_2by2_0_2.0}.pdf}
\caption{
Surface density maps of the gas (top left) and stellar (top right) components of \flower (accreting phase) and their radial velocity dispersion maps projected onto the $xy$-plane (bottom panels). Center of mass positions of MCCs within $\sim$1.5\,kpc of \flower identified with $n_{\rm cut}$\eq6.81\,\cc are overplotted as star symbols as an illustrative example.
\label{fig:sigma}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/{ss16_toomre_combined_3by1_0_1.2}.pdf}
\caption{
Toomre $Q$ maps derived from the central $R$\eq1.2\,kpc of \flower. Contribution from the gas ($Q_{\rm gas}$) and the stellar ($Q_\star$) components is shown in the left and middle panels, respectively. The effective two-component Toomre $Q_{\rm eff}$ parameter map is shown in the right panel.
%
All maps are projected onto the plane of the disk, and a gaussian smoothing of width 30\,pc has been applied to the maps.
%
Positions of MCCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ are overplotted as star symbols. Some MCCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, where regions of $\log{Q_{\rm eff}}\lesssim0$ are likely gravitationally unstable.
%
Close resemblance of the $Q_\star$ and $Q_{\rm eff}$ maps in the {\em central region} reflects the fact that stellar component plays an important role in governing the stability of MCCs against $m=0$  perturbations in relatively evolved and enriched systems at high redshifts.
\label{fig:Qeff}}
\end{figure*}

@@

@@

High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc. This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand, the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows. The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.
%
The variation in $\sigma_{\rm gas}^2/R$ with $\Sigma$ seen in this work is in line with previous studies, suggesting that ``Larson's third relation'' is an artifact arising from observational bias artifact of the limited range of  column densities a specific molecular line tracer is sensitive to \citep[][]{Ballesteros02a, Ballesteros11a}. This would imply column density is not a fundamental properties of molecular clouds and not all molecular clouds are virialized.

We perform virial analysis, as motivated by \obs, to assess the stability of MCCs. On average, the virial parameter of MCCs in the starburst phase of \flower is lower than in the accreting phase, as expected for \SF. Similarly, the virial parameter of MCCs identified at the highest density thresholds are lower than those identified at lower density thresholds.
% Toomre:
Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against axisymmetric perturbations, especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also non-negligible. This illustrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
%
Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates. This is consistent with the notion that collapsing structures result from gravitational instability occurring within globally stable structures, which are supported by turbulence and rotation on large scale.

This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies. Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
%
With the Next Generation VLA (ngVLA), which is approximately ten times more sensitive than ALMA, direct observations of molecular gas clouds in galaxies at the EoR on cloud scales will be possible via the higher-$J$ rotational transitions of CO in the 2030s.
% 0.005" highest freq
In the meantime, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
